Current and future constraints on primordial magnetic fields

### 2016-10-27 pmf.tex
a

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_knee.pdf}
  \caption[CMB polarization from PMFs]{
  Currently dummy plot.
  Will be plot of BB bandpowers and PMF template.
      \label{fig:pmf-bb}
  }
\end{figure*}

>>>>

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
  \caption[Current measurements of CMB B-modes]{
  Current measurements of CMB B-modes. \tbd{Caption to be updated}
      \label{fig:pmf-experiments}
  }
\end{figure*}

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
  \caption[CMB polarization from PMFs]{
  The expected contributions to CMB B-modes. 
  The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
  The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
  The dashed purple line shows the PMF template used in this work, scaled to \apmf{} = 0.2. 
  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal. 
  However PMFs also produce a vector component that peaks around $\ell \sim 1700$ and allows the discrimination between  the inflationary and PMF explanations. 
      \label{fig:pmf-bb}
  }
\end{figure*}
